---
title: "R Notebook"
output: html_notebook
---

Exercise: Write a script in R that solves a second degree equation
```{r}
a <- readline(prompt="Enter a number: ")
b<- readline(prompt="Enter a number: ")
c<- readline(prompt="Enter a number: ")
a=as.numeric(a)
b=as.numeric(b)
c=as.numeric(c)
if (a!=0){
  d=b^2-4*a*c
  if(d>0){
    x1=(-b+sqrt(d))/(2*a)
    x2=(-b-sqrt(d))/(2*a)
  print(x1,x2)
  }else if(d==0){
    x0=(-b)/(2*a)
    x0
  }else{
    print("impossible")
  }
}else{
  if(b!=0){
    x=-c/b
    x
  }else if(b==0 && c==0){
    print("undefined")
  }else{
    print("impossible")
  }
}
```

Exercise: Write a script in R that finds the roots of the function f (x) = 3 * X ^ 4-2 * x ^ 3 + 2 * x-1 in the interval [-10 ^ 6, 10 ^ 6] with step 0.5. As a root consider f (x) <= 0.05
```{r}

```

Exercise: create a vector with 150 random positive integers in interval
[1,20] by replacement. Create the frequency table without using the table command
```{r}
x=sample(1:20,150, replace = T)
table(x)
```

Exercise: Write a script with a function that accepts a positive integer and prints the value of its factorial
(e.g 5!=1*2*3*4*5=120)
```{r}
factorial<- function(){
n<- readline(prompt= "Enter a value: ")
n<- as.numeric(n)
fact=1
if(n< 0){
  print("The number is negative")
}else if( n==0){
  print("The factorial is 1")
}else(
  for(i in 1:n){
  fact = fact * i
  })
print(fact)
}

factorial()
```

Exercise: Create a matrix with 100 random  positive integers (25X4, rowsXcolumns) from a uniform distribution in space [1,3] by repositioning.
Then in each element of the table to create a column of relative frequencies using the apply command
```{r}
m <- matrix(runif(100,min=1,max=3),25,4)
m
```

Exercise: Create a 4-row and 5-column dataframe with real numbers (use rnorm()) and place NA value in 7 random positions using
the sample() function. Fill in the missing values with the total average of the dataframe
```{r}
z=matrix(rnorm(20,mean=0, sd=1),4 , 5)
p=matrix(rnorm(7,mean=0, sd=1),4,5)
z[p]=NA
z<-as.data.frame(z)
```

Exercise: Write a script in R that produces from uniform distribution 10000 random integers in space [1,100] and places them on a square matrix 100X100. Find the basic descriptive statistics of the table as a whole, by line and by column using simple commands (not using loops etc).
```{r}
un<-matrix(runif(1000, min= 1 , max=100),100, 100)
```

Exercise: remove rows containing missing values from the airquality dataset. Then, for the remaining rows select only those lines which had a temperature above 65F.(hint: use dplyr library)

```{r}
over65<- airquality%>%
  na.omit(airquality)%>%
  filter(Temp>65)
```

Exercise: from the mtcars dataset sort the rows of the horsepower column in descending order. Only the first 3 columns should be included in the results.
```{r}
mtcars%>%
  arrange(desc(mtcars$hp))%>%
  select(1:3)
  
```

Exercise: The aim of this exercise is to become more familiar with the dplyr package. Implement the following queries in R, using dplyr library functions.
a) Load the  mtcars dataset provided by R, and convert it so that its class is tbl_df.
b) Select the mpg, cyl and wt columns.
c) Filter the selected subset and keep only the records with cyl equal to 8. Then sort the records in ascending order in mpg and in descending order to wt.

```{r}

fm<-mtcars%>%
  tbl_df()%>%
  select(mpg, cyl, wt)%>%
  filter(cyl == 8)%>%
  arrange(mpg)%>%
  arrange(desc(wt))
```




